\speculake: Hiding Malware in Speculative Execution

### 2018-05-07 paper/implementation.tex
add speculating on data

>>>>

If the state is removed from cache, during the speculative execution the
state is also speculated. This error is particularly devious, as it is not an
error of bit flips, but rather the processor speculating what the state could
be, meaning that the state it uses is a possible value, and is not simply a
mutation.
